Predicting Fatalities in Toronto Car Crashes: Analyzing the Impact of Time, Vehicle Type, and Other Collision Determinants

### 2024-12-04 paper/paper.qmd
adjusted trace plots

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| fig-height: 15
#| fig-width: 20
#| label: fig-convergencecheckTrace
#| fig-cap: "Checking the convergence of the MCMC algorithm - Trace"

# Generate the trace plot
plot(prediction_model, "trace") + theme_minimal()
```

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| fig-height: 13
#| label: fig-convergencecheckRhat
#| fig-cap: "Checking the convergence of the MCMC algorithm - Rhat"
plot(prediction_model, "rhat") + theme_minimal()
```
## Model Results {#sec-appendix-results}

>>>>

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| fig-height: 13
#| fig-width: 10
#| label: fig-convergencecheckTrace
#| fig-cap: "Checking the convergence of the MCMC algorithm - Trace"

# Had to create my own trace plots because I couldn't adjust the formula
# Extract parameter names
trace_data <- as.data.frame(as.matrix(prediction_model))
params <- colnames(trace_data)
param_chunks <- split(params, ceiling(seq_along(params) / 20))

# Function to plot trace plots
plot_trace <- function(params_subset, data, title) {
  data %>%
    select(all_of(params_subset)) %>%
    pivot_longer(cols = everything(), names_to = "Parameter", values_to = "Value") %>%
    ggplot(aes(x = rep(1:nrow(data), length(params_subset)), y = Value, color = Parameter)) +
    geom_line() +
    facet_wrap(~ Parameter, scales = "free", ncol = 4) +  
    theme_minimal() +
    labs(title = title, x = "Iteration", y = "Value") +
    theme(legend.position = "none") + 
    theme(
      plot.margin = margin(t = 5, r = 5, b = 5, l = 10),  
      axis.text.x = element_text(size = 5, angle = 45, hjust = 1), 
      axis.text.y = element_text(size = 5), 
      plot.title = element_text(size = 10, hjust = 0.5), 
      strip.text = element_text(size = 7))
}

# Generate individual trace plots for each chunk
trace_plots <- list()
for (i in seq_along(param_chunks)) {
  trace_plots[[i]] <- plot_trace(
    params_subset = param_chunks[[i]],
    data = trace_data,
    title = paste("Trace Plots (Part", i, ")")
  )
}

grid.arrange(grobs = trace_plots, ncol = 2)
```

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| fig-height: 13
#| fig-width: 10
#| label: fig-convergencecheckRhat
#| fig-cap: "Checking the convergence of the MCMC algorithm - Rhat"
plot(prediction_model, "rhat") + theme_minimal()

## Model Results {#sec-appendix-results}

Please find the results to our model in @tbl-modelresults1, @tbl-modelresults2, and @fig-coefficient-estimates.
